Bayesian Evidence Synthesis:opioid crisis

### 2020-04-08 latex/newpaper.tex
generative model written

[\textbf{following the comment, the first attempt:}]\\  
The number of overdoses is our ultimate target of estimation. To achieve the goal in context of Bayesian statistics, we use our prior belief and available data set about the target of estimation. The posterior belief is coming from both of these sources of the information. Let $\theta$ denote all the unknown variables and let $Y$ denote all the related data sets. The following equation express the idea of Bayesian generative models in a mathmatical form:
\begin{equation}
\label{generic_bayes_thm}
\left.\begin{aligned}
p(\theta| Y ) = \frac{ p(\theta, Y)   }{ p(y)} = \frac{ p(\theta) p(Y|\theta)}{ p(Y)} \propto p(\theta) p(Y| \theta) \end{aligned}\right.
\end{equation}
[\textbf{Question: to make this flow better, maybe you want a  version of (1) which generically describes parameter and latent varaibles given observed data.}]
The equation \ref{generic_bayes_thm} states that the posterior belief of unobserved variables, $p(\theta|Y)$, is proportional to the mixture of the prior belief of the varaibles, $p(\theta)$, and the related data sets given the prior belief, $p(Y|\theta)$. Notice that the vector $\theta$ from equation \ref{generic_bayes_thm} includes parameters and latent variables, and hence it contains the total number of overdoses.

@@

>>>>

[\textbf{following the comment, the first attempt:}]\\  
The number of overdoses is our ultimate target of estimation. To achieve the goal in context of Bayesian statistics, we use our prior belief and available data set about the target of estimation. The posterior belief is coming from both of these sources of the information. Let $\theta$ denote all the unknown variables and let $Y$ denote all the related data sets. The following equation express the idea of Bayesian generative models in a mathmatical form:
\begin{equation}
\label{generic_bayes_thm}
\left.\begin{aligned}
p(\theta| Y ) = \frac{ p(\theta, Y)   }{ p(y)} = \frac{ p(\theta) p(Y|\theta)}{ p(Y)} \propto p(\theta) p(Y| \theta) \end{aligned}\right.
\end{equation}
[\textbf{Question: to make this flow better, maybe you want a  version of (1) which generically describes parameter and latent varaibles given observed data.}]
where $p(\cdot)$ is probability density (or mass) function. The equation \ref{generic_bayes_thm} states that the posterior belief of unobserved variables, $p(\theta|Y)$, is proportional to the mixture of the prior belief of the varaibles, $p(\theta)$, and the related data sets given the prior belief, $p(Y|\theta)$. Notice that the vector $\theta$ from equation \ref{generic_bayes_thm} includes parameters and latent variables, and hence it contains the total number of overdoses.

@@

\subsection{Generative Models}

[\textbf{draft:}] A generative model described in figure \ref{simple_draw} at a month $t$ can be written as follows given some a priori assumptions:

\begin{equation}
\label{gen_model}
\left.\begin{aligned}
p(\theta) & =p(\mu,\sigma^2,\lambda_t, N, O_t, p_{A,t}, n_{A,t}, x_{A,t}, U_t) \\
& = p(\mu)p(\sigma^2)p(\lambda_t|\mu, \sigma^2)p(N)p(O_t|\lambda_t, N)p(p_{A,t})p(n_{A,t})p(x_{A,t}|p_{A,t},n_{A,t})p(U_t|O_t, p_{A,t}) \\
& \propto p(\mu)p(\sigma^2)p(\lambda_t|\mu, \sigma^2)p(O_t|\lambda_t, N)p(p_{A,t})p(x_{A,t}|p_{A,t},n_{A,t})p(U_t|O_t, p_{A,t}) 
 \end{aligned}\right.
\end{equation}
